Application-Level Regression Testing Framework using Jenkins

### 2017-03-30 manuscript/manuscript.tex
expanded the securing jenkins section a bit

In addition, we restrict connections to OTP using pwauth and session control which is also in the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:
\begin{lstlisting}
# -- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
/usr/local/bin/pwauth+session
<LocationMatch / > 
AuthType Basic
AuthBasicProvider external
AuthName "NCSA RSA OTP login" 
AuthExternal pwauth+session
require valid-user  
RequestHeader unset "X-Forwarded-User"
RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>
\end{lstlisting}

The session control was implemented with a custom python script available here:
\begin{lstlisting}
/usr/local/bin/pwauth+session(OTP caching): 
https://github.com/reubendb/BasicAuthOTPSession
/blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}

OTP is configured by \texttt{/etc/pam.d/pwath}: 
\begin{lstlisting}
 #%PAM-1.0
auth  required  /lib64/security/pam_securid.so
account  include  password-auth
\end{lstlisting}

>>>>

In addition, we restrict connections to OTP using pwauth and session control. This is accomplished using the Apache module \texttt{mod_authnz_external} (FIXME: Add Reference) which is also in the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:
\begin{lstlisting}
# -- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
/usr/local/bin/pwauth+session
<LocationMatch / > 
AuthType Basic
AuthBasicProvider external
AuthName "NCSA RSA OTP login" 
AuthExternal pwauth+session
require valid-user  
RequestHeader unset "X-Forwarded-User"
RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>
\end{lstlisting}

Pwauth is called by \texttt{/etc/htpd/conf.d/authnz_external.conf}: 
\begin{lstlisting}
LoadModule authnz_external_module modules/mod_authnz_external.so
DefineExternalAuth pwauth pipe /usr/bin/pwauth
DefineExternalAuth pwauth+sssion pipe /usr/local/bin/pwauth+session
\end{lstlisting}

OTP is specified in \texttt{/etc/pam.d/pwauth}:
\begin{lstlisting}
#%PAM-1.0
auth	   required	/lib64/security/pam_securid.so
account    include      password-auth
\end{lstlisting}

The session control was implemented with a custom python script available here:
\begin{lstlisting}
/usr/local/bin/pwauth+session: 
https://github.com/reubendb/BasicAuthOTPSession
/blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}
